---
title: "Fitting the Dirichlet Process Mixture Model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dirichlet Process Mixture Model

The Dirichlet Process Mixture Model (DPMM) is used to identify latent clusters in the data. Unlike finite mixture models, the DPMM has no requirement on specifying the number of components *a priori*. An MCMC sampler is available from the R package `PReMiuM`, which allows for full customisation of prior hyperparameters. We choose $\kappa_0 = 4$ and leave other hyperparameters to their default values. We found that after some experimentation (not shown) that the value of $\kappa_0$ had some effect on the ability of the MCMC to explore the entire space, visiting modes.

```{r}
set.seed(123523)
library(PReMiuM)
library(Benchtools)
hyp <- setHyperparams(kappa0 = 4)
```

```{r}
processed_data <- readRDS(file = "../data/preprocessed-data.RDS")
data2017 <- processed_data$data2017
data2018 <- processed_data$data2018
reduced_variable_set <- processed_data$reduced_variable_set
```

```{r, cache=TRUE,results=FALSE,eval = TRUE}
profRegr_result <- profRegr_in_parallel(
  results_name = "../data/profRegr-results-D-fa", #name to give to results.
  n_chains = 6,
  n_cores = 6,
  start_seed = sample.int(10^9,size = 1),
  data = data2017[,reduced_variable_set],
  covNames = reduced_variable_set,
  xModel = 'Normal', excludeY = T,
  whichLabelSwitch = '3', sampler="SliceIndependent",
  varSelectType = 'None', # 'Continuous',
  nBurn = 10000, nSweeps = 200000,
  alpha = -2, hyp = hyp, nClusInit = 3,
  entropy = F, nProgress = 10, nFilter = 10
)
```

```{r, cache=TRUE,results=FALSE,eval = TRUE}
profRegr_result_2018 <- profRegr_in_parallel(
  results_name = "../data/profRegr-results-D-fa-2018", #name to give to results.
  n_chains = 6,
  n_cores = 6,
  start_seed = sample.int(10^9,size = 1),
  data = data2018[,reduced_variable_set],
  covNames = reduced_variable_set,
  xModel = 'Normal', excludeY = T,
  whichLabelSwitch = '3', sampler="SliceIndependent",
  varSelectType = 'None', # 'Continuous',
  nBurn = 10000, nSweeps = 200000,
  alpha = -2, hyp = hyp, nClusInit = 10,
  entropy = F, nProgress = 10, nFilter = 10
)
```

```{r,message=FALSE, warning=FALSE}
rmarkdown::render(output_file = "mcmc-diagnostics-2017.html",
                  input = "mcmc-diagnostic-template.Rmd",
                  params = list(
                    filepath = "../data/profRegr-results-D-fa",
                    set_title = "MCMC Diagnostics for DPMM fit to the 2017 Data"
                  ))

rmarkdown::render(output_file = "mcmc-diagnostics-2018.html",
                  input = "mcmc-diagnostic-template.Rmd",
                  params = list(
                    filepath = "../data/profRegr-results-D-fa-2018",
                    set_title = "MCMC Diagnostics for DPMM fit to the 2018 Data"
                  ))
```
